### 2016-06-09 sec1_introduction.tex
Some revisement
Section 4, Section 5 needs to merge

As can be seen, there are various co-movement patterns requested by different 
applications and it is cumbersome to design a tailored solution for each type. 
It is notable that \emph{platoon} pattern is able to represent other
patterns by setting appropriate parameters. However, we observe
that such a pattern definition, due to its overly-relaxed temporal constraints,
loses the fine control of a pattern
which leads to noisy results and unnecessary computations. We name this
scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
making the co-moving behavior very weak. In reality, 
such an anomaly is likely induced by the periodic movements of unrelated objects 
such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
In fact, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) 
are able to directly avoid such an anomaly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is valid in \emph{platoon}, \emph{swarm} and \emph{group} results.}
\label{fig:platoon_weakpoint}
\end{figure}

@@

The other issue with existing methods is that they are 
built on top of centralized indexes which face scalability challenges. 
To the best of our knowledge, the maximum number of trajectories
ever evaluated is up to a million data points.
In practice, it is rather common to collect hundreds of millions data points
and the scalabilities of current solutions are left unknown. 
We conduct a theoretical analysis on the worst-case complexity 
(as listed in Table~\ref{tbl:existing_co_patterns}) as well as 
an experimental evaluation with a real trajectory database 
with upto 2.4 million points (as shown in Figure~\ref{fig:related_work_scalability}). 
Results show that their performances degrade dramatically as the dataset scales up. For instances,
the performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
Therefore, directly applying these patterns on billion-scale real trajectories is impractical.

@@

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way while avoids 
the \emph{loose-connection} anomaly. In GCMP, we gain a
fine-grained control over pattern duration by introducing the gap 
parameter $G$, which enforces the gap between 
timestamps to be no larger than $G$.  
The adoption of $G$ seamlessly integrates with other pattern parameters,
which preserves the expressiveness while
alleviates the \emph{loose connection} anomalies.

@@

Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
of the partitions. Such properties ensure that neither false-patterns 
nor miss-patterns are possible in our solution. To meet such partition requirements
as well as to keep the shuffle amount to a minimum, 
we first design a naive \emph{Temporal Replication and Mining} (TRM)
approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
Despite the simpleness of star partition, we theoretically prove its optimality.
Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
shuffling and mining cost in SPM. 
%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
%Apache Spark which is one of the most popular MapReduce platforms.

@@

We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining; Section~\ref{sec:definition} forms the definition of the general co-movement pattern mining; Section~\ref{sec:system_overview} presents our parallel architecture; The solution of mining the general co-movement pattern mining is presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}. Section~\ref{sec:optimization} discuss various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to showcase the usefulness and efficiency of our system and finally Section~\ref{sec:conclusion} concludes our paper.

>>>>

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. In addition, despite the generality of the \emph{platoon} (i.e., it can be reduced to other types of patterns via proper parameter settings), it suffers from the so-called \emph{loose-connection} anomaly. We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario. These two objects form a \emph{platoon} pattern in timestamps $\{1,2,3,102,103,104\}$. However, the two consecutive segments are $98$ timestamps apart, resulting in a false positive co-movement pattern. In reality, such an anomaly may be caused  by the periodic movements of unrelated objects, such as vehicles stopping at the same petrol station or animals pausing at the same water source. 
Unfortunately, none of the existing patterns have directly addressed this anomaly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\{o_1, o_2: 1,2,3,102,103,104\}$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
% in \emph{platoon}, \emph{swarm} and \emph{group} results.
}
\label{fig:platoon_weakpoint}
\end{figure}

@@

The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance,
the detection time of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

@@

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. By setting a feasible $G$, the loose-connection anomaly can be avoided. In addition, our GCMP is both general and expressive. It can be reduced to any of the previous patterns by customizing the parameters.

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori method is adopted to mine the co-movement patterns. Third, we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

%
%Second, we investigate on deploying our GCMP detector to facilitate scalable pattern mining.
%In order to support large real trajectories, to the best of our knowledge, we
%are the first to study GCMP mining in MapReduce (MR) systems. There are a
%few challengers associated with designing an efficient MR-based pattern 
%detection algorithms. 
%
%First, in order to support effective parallelism, we need
%to partition the trajectory database with almost equal sizes. Our initial attempts
%develops a temporal based partition approached named as 
%\emph{Temporal Replication and Mining} (TRM). In TRM, neighboring snapshots form
%a equal-sized partition such that co-movement patterns can be mined independently.
%However, such a scheme require $O(|\mathbb{T}|)$ replication of input, which is 
%inefficient for large-scale trajectories. To support efficient mining, 
%we design a novel \emph{Star Partition and Mining} (SPM) approach which utilize
%the potential co-movement relationship among objects.
%
%Our initial attempt develops a naive but effective 
%\emph{Temporal Replication and Mining} (TRM) approach 
%which requires to replicate entire data set $O(|\mathbb{T}|)$ times. Such a 
%large set of

%There
%are a few challenges arises in designing the MR based pattern detection algorithm.
%First, we

%The major challenge
%we face is to make proper data partitions such
%that each partition can be efficiently processed independently. Our initial attempt develops
%a naive but effective \emph{Temporal Replication and Mining} (TRM) approach which requires to replicate
%entire data set $O(|\mathbb{T}|)$ times. To improve the efficiency, we design a novel \emph{Star Partition and Mining} (SPM)
%algorithm. In SPM, potential co-moving objects are first grouped into partitions. Subsequently,
%an apriori based method is applied to discover the patterns from each partition.
%Despite the simpleness of the star partition, we theoretically prove its correctness
%and optimality. Using SPM as the foundation, we develop and integrate
%a series of optimization techniques including \emph{edge simplification}, \emph{candidate pruning}
%and \emph{forward closure checking} to further boost the
%performances.
%

%
%Second, we investigate how to deploy our GCMP detector  on Spark for scalable pattern mining.
%The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
%In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
%of the partitions. Such properties ensure that neither false-patterns 
%nor miss-patterns are possible in our solution. To meet such partition requirements
%as well as to keep the shuffle amount to a minimum, 
%we first design a naive \emph{Temporal Replication and Mining} (TRM)
%approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
%method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
%Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
%as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
%a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
%GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
%Despite the simpleness of star partition, we theoretically prove its optimality.
%Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
%shuffling and mining cost in SPM. 
%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
%Apache Spark which is one of the most popular MapReduce platforms.

@@

We conduct a set of extensive experiments on XXX datasets with billion-scale trajectory points. The results show that XXX.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:system_overview} provides an overview of our parallel architecture. Solutions to mining the general co-movement patterns are presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}. Section~\ref{sec:optimization} discusses various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to verify the usefulness and efficiency of our system. Finally Section~\ref{sec:conclusion} concludes the paper.

### 2016-06-09 sec4_system.tex
Some revisement
Section 4, Section 5 needs to merge

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. In this section,
we briefly describe the preliminaries on MapReduce and then describe
the overview of our framework in mining GCMP.

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et.al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fault tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of three major steps: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Lastly,
reducers process the received data using a \emph{reduce} function.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since reducers are required to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
step requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration when designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
 $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
in map phase, trajectories are firstly reorganized by timestamps and object locations
at the same timestamps form a snapshot. In reduce phase, clustering of objects at each
snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters in each snapshot. We design and compare two MR algorithms (i.e., TRM and SPM)for 
GCMP mining. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

% corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
%of the first job is to cluster trajectories based on snapshots (i.e.,).
%As illustrated in (a), input trajectories are read in by mappers 
%and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
%form a snapshot. Then, a user defined clustering method is applied on the objects
%in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. 
%The second
%MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
%of the second job is to mine the GCMP from the snapshots computed in the first job. We design
%two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
%are first fed to mappers and different partition strategies may be selected to create
%partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
%The final computed results are then outputted to the end users.

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to the mappers at step (c). Therefore we do not need to 
transfer data between the two jobs. Modern MR platforms, especially Spark, have
already supported such a kind of pipeline.

\begin{figure} [t]
\center
\includegraphics[width=0.5\textwidth]{system_layout.eps}
\caption{System flow of mining GCMP. (a)(b) correspond to the first MR job which compute the clusters at each snapshot; 
(c)(d) correspond to the second MR jobs which mines GCMP in parrallel.}
\label{fig:overview}
\end{figure}

We note that the first MR job is easy to design since each reducer only
needs one snapshot for clustering.
In contrast, it is challenging to design the second job. 
This is because valid patterns may spray across multiple snapshots 
or contain different object sets, where inappropriate partitioning
of snapshots may fail to discover certain valid patterns.
Formally, a valid partition strategy 
needs to meet the following requirements: (a) the resulted partitions need
to preserve enough information so that real patterns can be discovered in the reduce phase. 
(b) the resulted partitions need to ensure that
the patterns discovered in the reduce phase are valid patterns so that
no further verification is required. We formalize these two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
\end{definition}
The completeness ensures that no true patterns are missed out. 
The soundness ensures that no false patterns are reported. 
If a partition method is both sound and complete, then it can be used
in the second MR job to facilitate GCMP mining.

Apparently, replicating the entire trajectories to each 
partition meets the \emph{soundness} and \emph{completeness} requirements. 
However, it burdens the network shuffle and limits the parallelism. 
Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
we present a novel \emph{object-based} partition-and-mining method
called \emph{Star Partition and Mining} (SPM) which resolves
the deficiencies of TRM method.

>>>>

\section{Temporal Replication and Mining}
\label{sec:trm}
We resort to the MapReduce (MR) paradigm for designing 
a parallel solution in mining GCMP. It is straightforward 
to partition the trajectory database into equal-sized 
temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
patterns may cross multiple temporal segments. In order to ensure
the correctness of results, we need to guarantee that
every valid patterns can be mined within at least 
one partitions.
Thus, some snapshots need to be 
replicated several times in multiple partitions. This
leads us to design the \emph{Temporal Replication and Mining}
(TRM) algorithm.

The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
In brief, there are two pipeline MR jobs which further consist of four stages. 
The first MR job is considered as a preprocessing, where input trajectories
are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
The output is shown as in Figure~\ref{fig:trm}(b). The second
MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
patterns from different partitions are then collected to form the output.

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first MR job which computes the clusters at each snapshot; 
(c)(d) correspond to the second MR job which uses TRM to mine GCMP in parallel.}
\label{fig:trm}
\end{figure*}

Since in the first MR job, each partition contains only one snapshot
for clustering, it is not necessary to replicate any snapshot. Thus, we
focus on describing the second MR job which is the \emph{Temporal
Replication and Mining} algorithm. We use $R$ to denote the replication factor.
The outline of TRM is 
shown in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
We will shortly discuss how the $R$ value is derived. 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $R$ times.
%\subsubsection{Temporal Replication Partition}
The replication factor $R$ is critical for the performance of TRM.
If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $R$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
later the correctness of this value.

%In the Algorithm~\ref{algo:trm_overview}, 
%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
%theorem, such a partition method is sound and complete.
%\begin{theorem}[Soundness and Completeness of Replication]
%\label{thm:replication_partition}
%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
%\end{theorem}
%\begin{proof}
%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$. This proves the completeness of the partitioning method.
%\end{proof}

\subsection{Line Sweep Mining}
Each task in the reduce phase processes a partition $Par_i$, which contains
$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
only the patterns whose object sets are contained in the first snapshot 
are necessary to be reported. Therefore, we design a simple 
\emph{line-sweep mining}(LSM) method for discovering
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

\begin{algorithm}
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $Par_t = \{S_t, S_{t+1}, ...\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\For{$c \in S_t$} 
\label{code:ls-init-start}
\State $C$.add($\langle c, t \rangle $)
\EndFor
\label{code:ls-init-end}
\ForAll{$i \in [1,R]$}
\State $N \gets S_{t+i} \oplus C$ \label{code:ls-join}
	\ForAll {$n \in N$}
		\If{$|n.O| \geq M$}
			$C$.add($n$).
			\label{code:ls-add}
		\EndIf
	\EndFor
\State{remove unqualified candidate from $C$}
	\label{code:ls-remove}
\EndFor
\State{output qualified candidate in $C$}
\end{algorithmic}
\end{algorithm}

The algorithm scans snapshots in a partition in sequence. During the scan, it
maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
The algorithm starts by inserting clusters at $S_i$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

%\begin{figure}[h]
%\centering
%\includegraphics[width=0.5\textwidth]{trm_process.eps}
%\caption{Work flow of trajectory replication and mining}
%\label{fig:trm_process}
%\end{figure}

\subsection{Correctness of TRM}
We prove the correctness of TRM from two aspects. First,
the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
not miss out any valid patterns. Second, no false patterns
are reported in any partitions. We formalize these two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
\end{definition}

Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
the following theorem to state the correctness:

\begin{theorem}[Correctness of Replication]
\label{thm:replication_partition}
Temporal replication partition is sound and complete.
\end{theorem}
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. For completeness, with a
valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
with the smallest length. Note that there could be many qualified $T'$s. 
Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
If every partition is of at least such a size, then $T'$ must be
captured by at least one of the partition. Thus, the pattern $P$ would 
be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the entire TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

%IMPORTANT!!!
%In contrast, it is challenging to design the second job. 
%This is because valid patterns may spray across multiple snapshots 
%or contain different object sets, where inappropriate partitioning
%of snapshots may fail to discover certain valid patterns.
%Formally, a valid partition strategy 
%needs to meet the following requirements: (a) the resulted partitions need
%to preserve enough information so that real patterns can be discovered in the reduce phase. 
%(b) the resulted partitions need to ensure that
%the patterns discovered in the reduce phase are valid patterns so that
%no further verification is required. We formalize these two 
%properties as \emph{completeness} and \emph{soundness} as follows:
%
%\begin{definition}[Completeness and Soundness]
%Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
%\end{definition}
%The completeness ensures that no true patterns are missed out. 
%The soundness ensures that no false patterns are reported. 
%If a partition method is both sound and complete, then it can be used
%in the second MR job to facilitate GCMP mining.
%
%Apparently, replicating the entire trajectories to each 
%partition meets the \emph{soundness} and \emph{completeness} requirements. 
%However, it burdens the network shuffle and limits the parallelism. 
%Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
%In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
%we present a novel \emph{object-based} partition-and-mining method
%called \emph{Star Partition and Mining} (SPM) which resolves
%the deficiencies of TRM method.
